---
title: "Experiment 2"
subtitle: "Self-Priority Effects on Nonspatial Working Memory"
author: "Woojeong Lee & Do-Joon Yi"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
      collapse: false
      smooth_scroll: false
    number_sections: true
    theme: cosmo 
    highlight: haddock
    code_folding: hide
mainfont: Noto Sans CJK KR
---

```{css, echo=FALSE}
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
```


```{r, collapse=TRUE}
pacman::p_load(tidyverse, psych, knitr, rstatix, BayesFactor)
pacman::p_load(ggpubr, see, cowplot)
pacman::p_load_gh("thomasp85/patchwork", 'eddjberry/mixturer')
if (!requireNamespace("Rmisc", quietly = TRUE)) install.packages("Rmisc")
if (!requireNamespace("bayestestR", quietly = TRUE)) install.packages("bayestestR")
if (!requireNamespace("magick", quietly = TRUE)) install.packages("magick")

set.seed(1234567) # for reproducibility
options(dplyr.summarise.inform=FALSE) # suppress warning in regards to regrouping 
options(knitr.kable.NA = '')
options("scipen" = 100) # https://rfriend.tistory.com/224
nIter <- 1e4 # Monte Carlo simulations for error < 1%. default = 1e4
tOff <- 2.5 # RTtrimming
klippy::klippy()

deg2rad <- function(deg){deg * pi / 180}

# Plot for outlier check
single_raincloud_plot <- function(df, Y, xMin, xMax, xBy, xLab){
  df %>% ggplot(aes(x = 1, y = Y)) +
    geom_violinhalf(flip = c(1,3), width = 0.5, color = "grey70", fill = "gray70") +
    geom_point(aes(0.8, Y), size = 1.5,
               color = "grey50", fill = "grey50", alpha = .5,
               position = position_jitter(width = 0.15, height = 0)) +
    geom_boxplot(width=0.05, alpha = 0.5, outliers = FALSE) +
    scale_y_continuous(breaks=seq(xMin,xMax,by=xBy)) +
    coord_flip(ylim = c(xMin, xMax), clip = "on") +
    labs(y = xLab) +
    theme_bw(base_size = 18) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.title.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          aspect.ratio = .3)
}

## Plot for results
plotMatchLabel <- function(df, ylabel, ymin, ymax, yby, 
                           OminusS, ymin2, ymax2, yby2) {
  names(df)[ncol(df)] <- "DV" # assuming DV on the last column
  
  df.g <- df %>%
    Rmisc::summarySEwithin(measurevar = 'DV', idvar = 'SN',
                           withinvars = c("Matching", "Label"))
  
  df.w <- df %>%
    unite("temp", c("Matching", "Label")) %>%
    pivot_wider(id_cols = SN, names_from = temp, values_from = DV)
  
  doff <- 0.03
  tmp <- runif(nrow(df.w), -doff, doff)
  spd1 <- rep(-0.14,nrow(df.w)) + tmp
  spd2 <- rep( 0.14,nrow(df.w)) + tmp
  
  F1 <- ggplot() +
    geom_bar(data=df.g, aes(x = Matching, y = DV, fill = Label), alpha = .6,
             stat="identity", width=0.7, linewidth=0.5, color="black", 
             position=position_dodge(.8)) +
    scale_fill_manual(values=c('#DC3220', '#005AB5'),
                      labels=c("Self", "Friend")) +
    geom_segment(data=df.w, color="black", alpha = 0.3, 
                 aes(x=1+spd1, y=Match_Self, xend=1+spd2, yend=Match_Friend)) +
    geom_segment(data=df.w, color="black", alpha = 0.3, 
                 aes(x=2+spd1, y=Nonmatch_Self, xend=2+spd2, yend=Nonmatch_Friend)) +
    geom_linerange(data=df.g, aes(x=Matching, ymin=DV-ci, ymax=DV+ci, group=Label),
                   linewidth=1, position=position_dodge(0.8)) +
    labs(x = "Matching", y = ylabel, fill='Label ') +
    coord_cartesian(ylim = c(ymin, ymax), clip = "on") +
    scale_y_continuous(breaks=seq(ymin, ymax, by = yby)) +
    theme_bw(base_size = 18) +
    theme(legend.position="top",
          legend.spacing.x = unit(0.5, 'lines'),
          legend.margin = margin(0, 0, 0, 0),
          legend.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())
  
  if (OminusS) { # Boolean: Friend - Self
    df2.w <- df.w %>% 
      mutate(Match = Match_Friend - Match_Self,
             Nonmatch = Nonmatch_Friend - Nonmatch_Self) %>% 
      select(SN, Match, Nonmatch)
  } else {
    df2.w <- df.w %>% 
      mutate(Match = Match_Self - Match_Friend,
             Nonmatch = Nonmatch_Self - Nonmatch_Friend) %>% 
      select(SN, Match, Nonmatch)
  }
  
  df2 <- df2.w %>% 
    pivot_longer(cols = c(Match, Nonmatch), names_to = "Matching", values_to = "SPE")
  
  df2.g <- df2 %>% 
    mutate(Matching = factor(Matching)) %>% 
    Rmisc::summarySEwithin(measurevar = "SPE", withinvars = "Matching", idvar = "SN")
  
  moff <- 0.1
  doff <- 0.05
  vpd <- rep(c(1-moff, 2+moff), nrow(df2)/2) # violin position dodge
  dpd <- rep(c(1+moff, 2-moff), nrow(df2)/2) + # dot position dodge
    rep(runif(nrow(df2)/2, -doff, doff), each=2)
  
  F2 <- cbind(df2, vpd, dpd) %>% 
    ggplot(aes(x = Matching, y = SPE, group = Matching)) + 
    geom_pointrange(data=df2.g, aes(x = Matching, ymin = SPE-ci, ymax = SPE+ci),
                    linewidth = 1, size = 0.5, color = "black") +
    geom_point(data=df2.g, aes(x = Matching, y = SPE),
               size=3, color = "black", show.legend = FALSE) +
    geom_hline(yintercept = 0) +
    geom_violinhalf(aes(x = vpd, y = SPE, group = Matching),
                    flip = c(1,3), width = 0.7, fill = "gray70") + 
    geom_line(aes(x = dpd, y = SPE, group = SN), color = "black", alpha = 0.3) +
    labs(x = "Matching",
         y = ifelse (OminusS, # Boolean: Friend - Self
                     "Friend - Self", "Self - Friend")) +
    coord_cartesian(ylim = c(ymin2, ymax2), clip = "on") +
    scale_y_continuous(breaks=seq(ymin2, ymax2, by = yby2)) +
    theme_bw(base_size = 18) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())
  
  F1 + F2 + plot_layout(nrow = 1, widths = c(2, 1.2))
}
```

The current experiment was preregistered on the [Open Science Framework ](https://osf.io/bvfw8). Participants completed an associative learning task followed by a working memory task.

<br>

---

<br>


# Associative Learning Task

The task was almost identical to that in Experiment 1. Each trial presented a red or blue shape with a superimposed social label—“당신” (the Korean word for “You”) or “친구” (the Korean word for “Friend”). Participants were asked to judge whether the color of the shape matched the color that had been associated with the referent of the label (self or friend) prior to the experiment. Participants used both hands to make label-matching responses: half pressed the leftmost button (of a 9-button response box) with the left hand for “Match” and the rightmost button with the right hand for “Nonmatch,” whereas the mapping was reversed for the other half of the participants. Accuracy was computed based on all responses, and response times (RTs) were analyzed only for correct label-matching responses.

## Label-Matching Accuracy

```{r, collapse=TRUE}
lrn <- read.csv("data/datSPE8VCS2LRN.csv", header = TRUE) %>% 
  mutate(SN = factor(SN),
         Matching = factor(Matching, 
                        levels = c("Match", "Nonmatch"), 
                        labels = c("Match", "Nonmatch")),
         Label = factor(Label, 
                        levels = c("Self", "Friend"), 
                        labels = c("Self", "Friend")),
         RT = RT * 1000)
str(lrn)
length(unique(lrn$SN))
table(lrn$SN)

# Accuracy
l.acc <- lrn %>% 
  group_by(SN, Matching, Label) %>% 
  summarise(Accuracy = mean(Correct)) %>% 
  ungroup()

plotMatchLabel(l.acc, "Accuracy", 0.5, 1, .1, FALSE, -.2, .3, .1)

# Descriptive
l.acc %>% group_by(Matching, Label) %>% 
  get_summary_stats(Accuracy, show = c("mean", "sd")) %>% 
  kable(digits = 2, format = "simple", caption = "Descriptive summary")

bias.acc <- l.acc %>% 
  filter(Matching == "Match") %>% 
  pivot_wider(id_cols = "SN", names_from = "Label", values_from = "Accuracy") %>% 
  mutate(selfBias = Self - Friend) %>% 
  select(SN, selfBias)

bias.acc %>% get_summary_stats(selfBias, show = c("mean", "sd")) %>% 
  kable(digits = 2, format = "simple", caption = "Match:Self - Match:Friend")
```

```{r, class.source = 'fold-show'}
bf.acc <- ttestBF(x = bias.acc$selfBias, rscale = 0.707)
bf.acc
```

The Bayes factor indicated that the data were more than `r format(extractBF(bf.acc)$bf[1], scientific = TRUE)` times more likely under the alternative hypothesis than under the null hypothesis.


## Label-Matching RT

```{r, collapse=TRUE}
range(lrn$RT[lrn$Correct==1])

lrn %>% 
  filter(Correct == 1) %>% 
  filter(RT < 200) %>% 
  summarise(N = n())

lt <- lrn %>% 
  filter(Correct == 1) %>% 
  group_by(SN) %>% 
  nest() %>%
  mutate(lbound = map(data, ~mean(.$RT)-tOff*sd(.$RT)),
         ubound = map(data, ~mean(.$RT)+tOff*sd(.$RT))) %>%
  unnest(c(lbound, ubound)) %>%
  unnest(data) %>%
  mutate(Outlier = (RT < lbound)|(RT > ubound)) %>%
  filter(Outlier == FALSE) %>%
  ungroup() %>%
  select(SN, Matching, Label,  RT)

table(lt$Matching, lt$SN)
table(lt$Label, lt$SN)
range(lt$RT)

tmp <- lt %>% 
  group_by(SN, Matching, Label) %>% 
  summarise(n = n()) %>% 
  ungroup() 
range(tmp$n) # check min & max number of trials.
tmp %>% 
  unite("Cond", Matching:Label) %>% 
  pivot_wider(id_cols = SN, names_from = Cond, values_from = n) %>% 
  print(n = Inf) # relatively high accuracy. seems enough number of trials.

( pTrmd <- 100*(sum(lrn$Correct) - nrow(lt))/sum(lrn$Correct) ) # proportion of trimmed RTs
```

Among correct responses, no trials had an RT faster than 200 ms. Correct RTs exceeding ±2.5 standard deviations from the subject-specific mean were excluded from analysis, accounting for `r round(pTrmd , digits = 2)`% of the data.

```{r, collapse=TRUE}
# RT
l.rt <- lt %>% 
  group_by(SN, Matching, Label) %>% 
  summarise(RT = mean(RT)) %>% 
  ungroup()

plotMatchLabel(l.rt, "Response Time (ms)", 400, 1100, 200, TRUE, -100, 250, 50)

# Descriptive
l.rt %>% group_by(Matching, Label) %>% 
  get_summary_stats(RT, show = c("mean", "sd")) %>% 
  kable(digits = 0, format = "simple", caption = "Descriptive summary")

bias.rt <- l.rt %>% 
  filter(Matching == "Match") %>% 
  pivot_wider(id_cols = "SN", names_from = "Label", values_from = "RT") %>% 
  mutate(selfBias = Friend - Self) %>% 
  select(SN, selfBias)

bias.rt %>% get_summary_stats(selfBias, show = c("mean", "sd")) %>% 
  kable(digits = 2, format = "simple", caption = "Match:Friend - Match:Self")
```

```{r, class.source = 'fold-show'}
bf.rt <- ttestBF(x = bias.rt$selfBias, rscale = 0.707)
bf.rt
```

The Bayes factor indicated that the data were more than `r format(extractBF(bf.rt)$bf[1], scientific = TRUE)` times more likely under the alternative hypothesis than under the null hypothesis.

<br>

---

<br>


# Working Memory Task

At the beginning of each trial, a blue and a red object appeared on the screen. Participants were required to briefly hold the colors and shapes of the objects in working memory. After a 2-second delay, a social label and a color wheel appeared along with a mouse cursor. Participants were asked to identify the shape of the object that had been presented in the color associated with the referent of the label.

```{r, fig.height=2}
ggdraw() + draw_image("fig/E2tst.png")
```

We measured the memory error (in a whole number from -179° to 180°) by calculating the angular deviation of a response from the ‘target’ shape cued by a label in each trial. As in Yin & Chen (2024), WM precision is then calculated separately for each participant and condition as the reciprocal of the standard deviation of memory errors across trials. The estimation of WM precision is based on the formula described in prior works ([Bays et al., 2009](https://jov.arvojournals.org/article.aspx?articleid=2122354)). 

## Precision

### Descriptive Stats

```{r, collapse=TRUE}
tst <- read.csv("data/datSPE8VCS2TST.csv") %>% 
  mutate(SN = factor(SN),
         Label = factor(Label, 
                        levels = c("Self", "Friend"), 
                        labels = c("Self", "Friend"))) %>% 
  mutate(ErrorRad = deg2rad(Error))
str(tst)
length(unique(tst$SN))
table(tst$selfColor, tst$SN)

range(tst$Error)
range(deg2rad(tst$Error))

headTail(tst)

# # Error는 아래 두 가지 방식으로 변인을 조합하여 재현할 수 있다.
# tst %>% mutate(tmp1 = (RspID - TrgID) %% 360,
#                tmp2 = ifelse(tmp1 > 180, tmp1-360, tmp1),
#                tmp3 = 1- (Error==tmp2)) %>%
#   summarise(sumError = sum(tmp3))
# 
# tst %>% mutate(tmp1 = (RspLoc - TrgLoc) %% 360,
#                tmp2 = ifelse(tmp1 > 180, tmp1-360, tmp1),
#                tmp3 = 1- (Error==tmp2)) %>%
#   summarise(sumError = sum(tmp3))


# Outlier Detection on precision

F3 <- tst %>% select(Label, ErrorRad) %>% 
  ggplot() +
  geom_histogram(mapping = aes(x = ErrorRad, 
                               y = after_stat(density), 
                               fill = Label),
                 position = 'identity', binwidth = pi/18, alpha = 0.4) +
  geom_density(mapping = aes(x = ErrorRad, color = Label),
               alpha = 0.5, linewidth = 0.5) +
  scale_x_continuous(breaks = c(-pi, -pi/2, 0, pi/2, pi),
                     label = c(expression(-pi), expression(-pi/2),
                               0, expression(pi/2), expression(pi))) +
  labs(x = "Memory Error (rad)", y = "Density") +
  # facet_grid(. ~ Label) +
  scale_fill_manual(values=c("#DC3220", "#005AB5")) +
  scale_color_manual(values=c("#DC3220", "#005AB5")) +
  theme_bw(base_size = 18) +
  theme(legend.position="top",
        legend.spacing.x = unit(0.5, 'lines'),
        legend.margin = margin(0, 0, 0, 0),
        legend.background = element_blank(),
        strip.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

t1 <- tst %>% 
  group_by(SN, Label) %>% 
  group_modify( ~ bays_2009_error(.$ErrorRad)) %>% 
  ungroup() %>%
  rename(Precision = precision)
headTail(t1)
t1 %>% print(n = Inf)

t1.g <- t1 %>%
  Rmisc::summarySEwithin(measurevar = 'Precision', idvar = 'SN',
                         withinvars = "Label")
t1.w <- t1 %>%
  pivot_wider(id_cols = SN, names_from = Label, values_from = Precision)

pd <- rep(c(1.1, 1.9), 72)
F4 <- ggplot() +
  geom_bar(data=t1.g, aes(x = Label, y = Precision, fill = Label), alpha = .6,
           stat="identity", width=0.7, linewidth=0.5, color="black") +
  # geom_point(data=cbind(t1, pd), aes(x = pd, y = Precision, group = Label),
  #            color="gray80", alpha=0.5, size=1.8) +
  geom_segment(data=t1.w, color="black", alpha=0.3,
               aes(x=1+.1, y=Self, xend=2-.1, yend=Friend)) +
  geom_linerange(data=t1.g, aes(x=Label, ymin=Precision-ci, ymax=Precision+ci, group=Label),
                 linewidth=1) +
  # geom_point(data=t1.g, aes(x = Label, y = Precision),
  #            size=3, color = "black", show.legend = FALSE) +
  scale_fill_manual(values=c('#DC3220', '#005AB5'),
                    labels=c("Self", "Friend")) +
  labs(x = "Label", y = expression("Precision (" * rad^{-1} * ")")) +
  coord_cartesian(ylim = c(0, 5), clip = "on") +
  scale_y_continuous(breaks=seq(0, 5, by = 1)) +
  theme_bw(base_size = 18) +
  theme(legend.position= "none",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
# , position = position_nudge(x = .1, y = 0)

F3 + F4 + plot_layout(nrow = 1, widths = c(1, 1))

# Descriptive
t1 %>% group_by(Label) %>% 
  get_summary_stats(Precision, show = c("mean", "sd")) %>% 
  kable(digits = 2, format = "simple", caption = "Descriptive summary")

```

### Bayes Factor 

```{r, class.source = 'fold-show'}
bf1 <- ttestBF(t1.w$Self - t1.w$Friend,
               rscale = 0.707, # = 'medium',
               nullInterval = c(0, Inf))
bf1
1/bf1[1]
```

The Bayes factor indicated that the data were more than `r 1/extractBF(bf1)$bf[1]` times more likely under the null hypothesis than under the directional alaternative hypothesis.

```{r, collapse=TRUE, fig.height=3}
plot(bayestestR::bayesfactor_models(bf1[1])) + 
  scale_fill_pizza() +
  scale_fill_manual(values=c('#E69F00', '#56B4E9')) +
  theme(text = element_text(size = 18))
```

<br>

---

<br>

# Correlation

Self-bias were computed separately for label-matching RTs in the associative learning task and for precision in the working memory task. 

For label-matching RTs, self-bias was defined as the difference between the self and friend conditions on match trials, following prior research ([Yin et al., 2019](https://doi.org/10.1177/0956797618818483)). For WM precision, it was defined as the difference between the self and friend conditions.

A Pearson correlation was then calculated between the two self-bias measures.

```{r, collapse=TRUE}
lrn.matching <- l.rt %>% 
  filter(Matching == "Match") %>% 
  pivot_wider(id_cols = SN, names_from = Label, values_from = RT) %>%
  mutate(lrnLabel = Friend - Self) %>%
  select(SN, lrnLabel)

tst.precision <- t1 %>% 
  pivot_wider(id_cols = SN, names_from = Label, values_from = Precision) %>% 
  mutate(wmShape = Self - Friend) %>% 
  select(SN, wmShape)

spe.effects <- full_join(
  lrn.matching, tst.precision, by = 'SN') 
# spe.effects %>% print(n = Inf)
```


```{r, class.source = 'fold-show'}
# https://cran.r-project.org/web/packages/BayesFactor/vignettes/manual.html#lincor
bf2 <- correlationBF(x = spe.effects$lrnLabel, 
                    y = spe.effects$wmShape, rscale = 0.707)
bf2
```

The Bayes factor indicated that the data were more than `r 1/extractBF(bf2)$bf[1]` times more likely under the null hypothesis than under the directional alaternative hypothesis.

```{r, collapse=TRUE}
# cor.test(x = spe.effects$lrnLabel, y = spe.effects$wmShape)
spe.effects %>% cor_test(lrnLabel, wmShape) %>% 
  mutate("95% CI" = paste0("[", round(conf.low, digits = 3), ", ",
                                 round(conf.high, digits = 3), "]")) %>%
  select(var1, var2, method, cor, '95% CI', statistic, p) %>% 
  rename(Variable1 = var1, Variable2 = var2, r = cor) %>% 
  kable(digits = 3, format = "simple", align = "llrrrrr", caption = "Correlation")
```

```{r, collapse=TRUE}
bf2 %>% bayestestR::describe_posterior()

C1 <- ggplot(spe.effects, aes(x=lrnLabel, y=wmShape)) +
  geom_point(size = 3, alpha = 0.5) +
  geom_smooth(method=lm, formula = y ~ x) +
  labs(x = expression(paste("Self-Bias" [" AL Task"])), 
       y = expression(paste("Self-Bias" [" WM Task"]))) +
  theme_bw(base_size = 18) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        aspect.ratio = 1) +
  annotate(geom = "text", x = 50, y = -2.2, hjust = 0, size = 5,
           label = "paste(italic(r), \" = .21, \", italic(p), \" = .07\")", 
           parse = TRUE)
C2 <- plot(bayestestR::bayesfactor_models(bf2)) + 
  scale_fill_pizza() +
  scale_fill_manual(values=c('#E69F00', '#56B4E9')) +
  theme(text = element_text(size = 18))

C1 + C2 + plot_layout(nrow = 1, widths = c(1.5, 1))
```


---


# Session Info

```{r session_info, collapse=TRUE}
sessionInfo()
```
